### 2019-11-27 README.Rmd
akaike_weights
gosset

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
options(width = 120)
```

@@

@@

You are welcome to contribute to this project. Please read our [contribution guide lines](CONTRIBUTING.md).

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(width = 120)
```

@@

# _gosset_: Modelling Metadata and Experimental Citizen Science <img align="right" src="man/figures/logo.png">

@@

You are welcome to contribute to this project. Please read our [contribution guideline](CONTRIBUTING.md).
